A meta-analysis of the impacts of best management practices on nonpoint source pollutant concentration.

### 2024-06-10 frontiers_submission/frontiers_submission_revision_02.Rmd
fix typo in table 1

tibble(
  "Attribute" = c("Study type", "Outcomes", "Geographical context", "Timeframe"),
  "Inclusion Criteria" = c("Journal articles, book chapters, conference papers, unpublished research reports, thesis and dissertations, organizational and agency white papers.",
                           "Field studies with measured effects on fecal indicator bacteria or nutrient concentrations.",
                           "Studies conducted within the United States.",
                           "Studies published from 2000 through 2022."),
  "Excluision Criteria" = c("Synopsis or review studies, reports with reductions based on modeled or other estimated reductions (e.g. TMDLs, watershed plans, or modelling studies.",
                            "Studies not explicitly linking concentration reductions to a specific BMP or insufficient information to quantify reductions.",
                            "Studies outside of the United States.",
                            "Studies published prior to 2000 or after 2022.")
) |> 
  kableExtra::kbl(booktabs = TRUE,
                  caption = "Criteria applied for including or excluding studies within the review database.") |> 
  kableExtra::kable_styling(full_width = FALSE) |>
  kableExtra::column_spec(1, width = "5em") |> 
  kableExtra::column_spec(2, width = "15em") |> 
  kableExtra::column_spec(3, width = "15em")

>>>>

tibble(
  "Attribute" = c("Study type", "Outcomes", "Geographical context", "Timeframe"),
  "Inclusion Criteria" = c("Journal articles, book chapters, conference papers, unpublished research reports, thesis and dissertations, organizational and agency white papers.",
                           "Field studies with measured effects on fecal indicator bacteria or nutrient concentrations.",
                           "Studies conducted within the United States.",
                           "Studies published from 2000 through 2022."),
  "Exclusion Criteria" = c("Synopsis or review studies, reports with reductions based on modeled or other estimated reductions (e.g. TMDLs, watershed plans, or modelling studies.",
                            "Studies not explicitly linking concentration reductions to a specific BMP or insufficient information to quantify reductions.",
                            "Studies outside of the United States.",
                            "Studies published prior to 2000 or after 2022.")
) |> 
  kableExtra::kbl(booktabs = TRUE,
                  caption = "Criteria applied for including or excluding studies within the review database.") |> 
  kableExtra::kable_styling(full_width = FALSE) |>
  kableExtra::column_spec(1, width = "5em") |> 
  kableExtra::column_spec(2, width = "15em") |> 
  kableExtra::column_spec(3, width = "15em")
